---
title: Using the 'TABUS' C++ Reshaper
author: Christian "Small-Plate" Testa
output: html_document
---

```{r}
library(MITUS)
devtools::load_all()
# model_load('US')
# load(system.file('US/US_parAll10_2018-12-10.rda', package='MITUS')) # input parameters

model_load('CA')
load(system.file("CA/parAll_CA_10_2018_11_27.rds", package='MITUS'))

out <- OutputsZint(1, 
	    ParMatrix=ParMatrix, 
	    startyr=1950,
	    endyr=2050,
	    Int1=0,
	    Int2=0,
	    Int3=0,
	    Int4=0,
	    Int5=0,
	    Scen1=0,
	    Scen2=0,
	    Scen3=0)
```

Define the original `format_as_restab` for double-checking our results.

```{r}
format_as_restab <- function(o) { 

  age_id = (2018:2049)-1949
  tt<-0
  #create 3 lists to hold output
  ResTabfb <- ResTabus <- ResTab <- array(NA,dim=c(10,length(age_id),7,11))

	# For now just set intv = 1 for a base-case scenario, but later we need to change this
	# to reflect that we're working on custom scenarios
	intv <- 1

	#dimensions of restab are:
	#number of datasets, number of ages, number of interventions
	nr<-10
	#gather the outputs from that model run
	for (ag in 1:11){
		################################################################################
		#total population
		#dimensions are
		#scenarios; length age id;
		# print(1:nr+((intv-1)*10))
		################################################################################
		ResTab[1:nr+((intv-1)*10),,1,ag]<-o[age_id,1]
		#number of ltbi prevalence
		ResTab[1:nr+((intv-1)*10),,2,ag]<-apply(o[age_id,c(54,65)+ag],c(1,2),sum)*1e3
		#percentage of ltbi prevalence
		ResTab[1:nr+((intv-1)*10),,3,ag]<-apply(o[age_id,c(54,65)+ag],c(1,2),sum)/o[age_id,32+ag]*1e2
		#TB notifications (alive+dead at diagnosis)
		ResTab[1:nr+((intv-1)*10),,4,ag]<-apply(o[age_id,c(135,188)+ag],c(1,2),sum)*1e3
		#percentage TB notifications (alive+dead at diagnosis)
		ResTab[1:nr+((intv-1)*10),,5,ag]<-apply(o[age_id,c(135,188)+ag],c(1,2),sum)/o[age_id,32+ag]*1e2
		#tb attributable deaths
		ResTab[1:nr+((intv-1)*10),,6,ag]<-apply(o[age_id,c(87,98)+ag],c(1,2),sum)*1e3
		# percentage tb attributable deaths
		ResTab[1:nr+((intv-1)*10),,7,ag]<-apply(o[age_id,c(87,98)+ag],c(1,2),sum)/o[age_id,32+ag]*1e2

		################################################################################
		#US Born population
		################################################################################
		ResTabus[1:nr+((intv-1)*10),,1,ag]<-o[age_id,1]
		#number of ltbi prevalence
		ResTabus[1:nr+((intv-1)*10),,2,ag]<-o[age_id,54+ag]*1e3
		#percentage of ltbi prevalence
		ResTabus[1:nr+((intv-1)*10),,3,ag]<-o[age_id,54+ag]/o[age_id,43+ag]*1e2
		#TB notifications (alive+dead at diagnosis)
		ResTabus[1:nr+((intv-1)*10),,4,ag]<-apply(o[age_id,c(204,215)+ag],c(1,2),sum)*1e3
		#percentage TB notifications (alive+dead at diagnosis)
		ResTabus[1:nr+((intv-1)*10),,5,ag]<-apply(o[age_id,c(204,215)+ag],c(1,2),sum)/o[age_id,43+ag]*1e2
		#tb attributable deaths
		ResTabus[1:nr+((intv-1)*10),,6,ag]<-o[age_id,87+ag]*1e3
		# percentage tb attributable deaths
		ResTabus[1:nr+((intv-1)*10),,7,ag]<-o[age_id,87+ag]/o[age_id,43+ag]*1e2

		################################################################################
		#non-US Born population
		################################################################################
		ResTabfb[1:nr+((intv-1)*10),,1,ag]<-o[age_id,1]
		#number of ltbi prevalence
		ResTabfb[1:nr+((intv-1)*10),,2,ag]<-o[age_id,65+ag]*1e3
		#percentage of ltbi prevalence
		ResTabfb[1:nr+((intv-1)*10),,3,ag]<-o[age_id,65+ag]/o[age_id,2+ag]*1e2
		#TB notifications (alive+dead at diagnosis)
		ResTabfb[1:nr+((intv-1)*10),,4,ag]<-(apply(o[age_id,c(135,188)+ag],c(1,2),sum)-apply(o[age_id,c(204,215)+ag],c(1,2),sum))*1e3
		#percentage TB notifications (alive+dead at diagnosis)
		ResTabfb[1:nr+((intv-1)*10),,5,ag]<-(apply(o[age_id,c(135,188)+ag],c(1,2),sum)-apply(o[age_id,c(204,215)+ag],c(1,2),sum))/o[age_id,43+ag]*1e2
		#tb attributable deaths
		ResTabfb[1:nr+((intv-1)*10),,6,ag]<-o[age_id,98+ag]*1e3
		# percentage tb attributable deaths
		ResTabfb[1:nr+((intv-1)*10),,7,ag]<-o[age_id,98+ag]/o[age_id,2+ag]*1e2
	}

  return(list(
							ResTab = ResTab,
							ResTabus = ResTabus,
							ResTabfb = ResTabfb
							))
}
```

Generate the ResTabC list containing 3 (4D) objects: ResTab, ResTabus, ResTabfb

```{r}
ResTabC <- format_as_restab(out)
```

Generate res_tab2 dataframe (without data yet)

```{r}
make_empty_res_tab2 <- function() {
	# Specify the levels of each dimension to the data
	CatList <- list()
	CatList[[1]] <- c(
		"ltbi_000s",
		"pct_ltbi",
		"tb_incidence_000s",
		"tb_incidence_per_mil",
		"tb_mortality_000s",
		"tb_mortality_per_mil")
	CatList[[2]] <- c('base_case')
	CatList[[3]] <- c("all_populations","usb_population","fb_population")
	CatList[[4]] <- c("0-4",paste(0:8*10+5,1:9*10+4,sep="-"),"95+")
	CatList[[5]] <- c("absolute_value","pct_basecase_same_year","pct_basecase_2016")
	CatList[[6]] <- 2018:2049
	# CatList[[7]] <- c("mean","ci_low","ci_high")

	# Make the specified levels integer-leveled factors
	CatList_factors <- lapply(CatList, function(x) {
		factor(x=1:length(x), levels=1:length(x), labels=x) })

	# Turn the integer-factors into all possible combinations in a dataframe
	# with an extra column of NA values for a 'value' column
	res_tab2 <-  cbind(expand.grid(CatList_factors),NA)

	# Name the columns
	colnames(res_tab2) <- c(
		"outcome",
		"scenario",
		"population",
		"age_group",
		"comparator",
		"year",
		"value")

	return(res_tab2)
}
```

Specify the original reshaper function in R
```{r}
original_reshaper <- function(ResTabC) {
	res_tab2 <- make_empty_res_tab2()

  for (it in 1:nrow(res_tab2)) {
    i1 <- as.integer(res_tab2[it,'outcome'])
    i2 <- as.integer(res_tab2[it, 'scenario'])
    i3 <- as.integer(res_tab2[it, 'population'])
    i4 <- as.integer(res_tab2[it, 'age_group'])
    i5 <- as.integer(res_tab2[it, 'comparator'])
    i6 <- as.integer(res_tab2[it, 'year'])
    i7 <- as.integer(res_tab2[it, 'statistic'])

    res_tab2[it, 'value'] <-
      switch(
        as.character(res_tab2[it, 'comparator']),
        'absolute_value' = {
          ResTabC[[i3]][i2, i6, i1 + 1, i4]
        },
        'pct_basecase_same_year' = {
          ResTabC[[i3]][i2, i6, i1 + 1, i4] /
            ResTabC[[i3]][1, i6, i1 + 1, i4] * 100
        },
        'pct_basecase_2016' = {
          ResTabC[[i3]][i2, i6, i1 + 1, i4] /
            ResTabC[[i3]][1, i6, 1, i4] * 100
        }
      )
  }
	return(res_tab2)
}
```


Now let's test to see if we get the same outcomes from each of our reshapers.
```{r}
res_tab2_1 <- original_reshaper(ResTabC)

# Make an empty res_tab2 for comparison to res_tab2_1
library(dplyr)
res_tab2_2 <- make_empty_res_tab2()
# convert to a matrix with integer values where levels would be
res_tab2_2 %<>% mutate_if(is.factor, as.integer) %>% as.matrix

# Import the C++ Reshaper
library(inline)
# We use readr to ensure that the UTF8 encoding of the .cpp file is preserved, 
# newlines are interpreted properly, etc. Other approaches, such as using readLines 
# don't automatically respect newlines and tabs properly.
cpp_reshaper <- cxxfunction(
	signature(ResTab='numeric', ResTabus='numeric', ResTabfb='numeric', res_tab2 = 'numeric'),
	plugin='Rcpp',
	body=readr::read_file(
		system.file('inline_cpp/format_restab2.cpp', package='tabus')))

res_tab2_2 <- cpp_reshaper(ResTabC$ResTab, ResTabC$ResTabus, ResTabC$ResTabfb, res_tab2_2)
```


Now we do our final test! Do we get exactly the same results? 0 indicates yes!
```{r}
if(max(res_tab2_1[,'value'] - res_tab2_2[,'value']) == 0) {
	print('SUCCESS!')
} else print(':(')
```

If one wants to format the `res_tab2_2` object to be filled with characters instead of integers, we just have to re-factor it. 

```{r}
	# Specify the levels of each dimension to the data
	CatList <- list()
	CatList[[1]] <- c(
		"ltbi_000s",
		"pct_ltbi",
		"tb_incidence_000s",
		"tb_incidence_per_mil",
		"tb_mortality_000s",
		"tb_mortality_per_mil")
	CatList[[2]] <- c('base_case')
	CatList[[3]] <- c("all_populations","usb_population","fb_population")
	CatList[[4]] <- c("0-4",paste(0:8*10+5,1:9*10+4,sep="-"),"95+")
	CatList[[5]] <- c("absolute_value","pct_basecase_same_year","pct_basecase_2016")
	CatList[[6]] <- 2018:2049


# Format as a dataframe
res_tab2_2 <- as.data.frame(res_tab2_2)

# 'Factorize' each column
for (i in 1:6) {
	res_tab2_2[,i] <- factor(res_tab2_2[,i], labels = CatList[[i]])
}

# Print for validation and comfort of mind
head(res_tab2_2)
```

